Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-10-17 papers/termination/termination-esop/paper.tex
removed synthesis refinement loop figure

\begin{figure}
 \begin{center}
 \resizebox{\linewidth}{!}{%
  \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,
 semithick, initial text=]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=1cm, minimum width=1.5cm},
          row sep=2cm, column sep=2.5cm, ampersand replacement=\&] {
   \node (synth) {Synthesise};
   \&
   \node (verif) {Verify}; %\\
   %\node[draw=none] {};
   \&
   \node[ellipse] (done) {Done}; \\
  };

   \path
    (synth) edge [bend left] node {Candidate program} (verif)
    (verif) edge [bend left] node {Counterexample input} (synth)
    (verif) edge node {Valid} (done);
 \end{tikzpicture}
 }
 \end{center}

 \caption{Abstract synthesis refinement loop
 \label{fig:abstract-refinement}}
\end{figure}

>>>>

%% \begin{figure}
%%  \begin{center}
%%  \resizebox{\linewidth}{!}{%
%%   \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,
%%  semithick, initial text=]

%%   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=1cm, minimum width=1.5cm},
%%           row sep=2cm, column sep=2.5cm, ampersand replacement=\&] {
%%    \node (synth) {Synthesise};
%%    \&
%%    \node (verif) {Verify}; %\\
%%    %\node[draw=none] {};
%%    \&
%%    \node[ellipse] (done) {Done}; \\
%%   };

%%    \path
%%     (synth) edge [bend left] node {Candidate program} (verif)
%%     (verif) edge [bend left] node {Counterexample input} (synth)
%%     (verif) edge node {Valid} (done);
%%  \end{tikzpicture}
%%  }
%%  \end{center}

%%  \caption{Abstract synthesis refinement loop
%%  \label{fig:abstract-refinement}}
%% \end{figure}
